Part B-2

### 2023-05-02 msca-pf-part-b1-template.tex
rename project to msca-pf
update to 2023 call and v3 of the template

\documentclass[11pt,draftproposal]{msca-pf-2022}
% {{{ packages

@@

\begin{itemize}
    \item Describe the quality and pertinence of the R \& I objectives; are the
    objectives measurable and verifiable? Are they realistically achievable?

@@

        \item  Sex, gender and diversity analysis refers to biological
        characteristics and social/cultural factors respectively. For guidance on
        methods of sex / gender analysis and the issues to be taken into account,
        please refer to
        \href{https://ec.europa.eu/info/news/gendered-innovations-2-2020-nov-24_en}{this page}.
    \end{itemize}

@@

    \item \emph{Open science is an approach based on open cooperative work and systematic
    sharing of knowledge and tools as early and widely as possible in the process.
    Open science practices include early and open sharing of research (for example
    through pre-registration, registered reports, pre-prints, or crowd-sourcing);
    research output management; measures to ensure reproducibility of research
    outputs; providing open access to research outputs (such as publications,
    data, software, models, algorithms, and workflows); participation in open
    peer-review; and involving all relevant knowledge actors including citizens,
    civil society and end users in the co-creation of R\&I agendas and contents
    (such as citizen science).}

    \item \emph{Please note that this does not refer to outreach actions that may be
    planned as part of the communication, dissemination and exploitation activities.
    These aspects should instead be described below under ``Impact''.}

@@

    \item \emph{For guidance on open science practices and research data management,
    please refer to the relevant section of the \href{https://ec.europa.eu/info/funding-tenders/opportunities/docs/2021-2027/horizon/guidance/programme-guide_horizon_en.pdf}{HE Programme Guide}
    on the Funding \& Tenders Portal.}
\end{itemize}

@@

\begin{itemize}
    \item \emph{Expected} skill development of the researcher.
    \item \emph{Expected} impact of the proposed research and training activities on
    the researcher's career perspectives inside and/or outside academia.
\end{itemize}

@@

    \item Be specific, referring to the effects of your project, and not R\&I
    in general in this field. State the target groups that would benefit.

    \begin{itemize}
        \item \emph{Expected scientific impact(s)}: e.g. contributing to specific
        scientific advances, across and within disciplines, creating new knowledge,
        reinforcing scientific equipment and instruments, computing systems (i.e.
        research infrastructures);

@@

    \item Give an indication of the magnitude and importance of the project's
    contribution to the expected outcomes and impacts, should the project be
    successful. Provide quantified estimates where possible and meaningful.
    ``Magnitude'' refers to how widespread the outcomes and impacts are likely
    to be. For example, in terms of the size of the target group, or the
    proportion of that group, that should benefit over time; ``Importance''
    refers to the value of those benefits. For example, number of additional
    healthy life years; efficiency savings in energy supply.
\end{itemize}

>>>>

\documentclass[11pt,draftproposal]{msca-pf}
% {{{ packages

@@

\begin{itemize}
    \item Describe the quality and pertinence of the R\&I objectives; are the
    objectives measurable and verifiable? Are they realistically achievable?

@@

        \item  Sex, gender and diversity analysis refers to biological
        characteristics and social/cultural factors respectively. For guidance on
        methods of sex / gender analysis and the issues to be taken into account,
        please refer to
        \href{https://ec.europa.eu/info/news/gendered-innovations-2-2020-nov-24_en}{this page}.

        \item If you plan to use, develop and/or deploy artificial intelligence
        (AI) based systems and/or techniques you must demonstrate their technical
        robustness. AI-based systems or techniques should be, or be developed to
        become:

        \begin{itemize}
            \item technically robust, accurate and reproducible, and able to
            deal with and inform about possible failures, inaccuracies and
            errors, proportionate to the assessed risk they pose,

            \item socially robust, in that they duly consider the context and
            environment in which they operate,

            \item reliable and function as intended, minimizing unintentional
            and unexpected harm, preventing unacceptable harm and safeguarding
            the physical and mental integrity of humans,

            \item able to provide a suitable explanation of their decision-making
            processes, whenever they can have a significant impact on people’s
            lives.
        \end{itemize}
    \end{itemize}

@@

    \emph{Open science is an approach based on open cooperative work and systematic
    sharing of knowledge and tools as early and widely as possible in the process.
    Open science practices include early and open sharing of research (for example
    through pre-registration, registered reports, pre-prints, or crowd-sourcing);
    research output management; measures to ensure reproducibility of research
    outputs; providing open access to research outputs (such as publications,
    data, software, models, algorithms, and workflows); participation in open
    peer-review; and involving all relevant knowledge actors including citizens,
    civil society and end users in the co-creation of R\&I agendas and contents
    (such as citizen science).}

    \emph{Please note that this does not refer to outreach actions that may be
    planned as part of the communication, dissemination and exploitation activities.
    These aspects should instead be described below under ``Impact''.}

@@

    \emph{For guidance on open science practices and research data management,
    please refer to the relevant section of the \href{https://ec.europa.eu/info/funding-tenders/opportunities/docs/2021-2027/horizon/guidance/programme-guide_horizon_en.pdf}{HE Programme Guide}
    on the Funding \& Tenders Portal.}

    Please also see the “how to evaluate open science in Horizon Europe proposals”
    video on the \href{https://ec.europa.eu/info/funding-tenders/opportunities/portal/screen/support/videos}{Funding \& Tenders portal}.
\end{itemize}

@@

\begin{itemize}
    \item Specific measures to enhance career perspectives and employability of
    the researcher inside and/or outside academia.
    \item \emph{Expected} contribution of proposed skills development to the
    future career of the researcher.
\end{itemize}

@@

    \item Be specific, referring to the effects of your project, and not R\&I
    in general in this field. State the target groups that would benefit.
Partial alignment of text with standard application form template for criteria 2.3
    \begin{itemize}
        \item \emph{Expected scientific impact(s)}: e.g. contributing to specific
        scientific advances, across and within disciplines, creating new knowledge,
        reinforcing scientific equipment and instruments, computing systems (i.e.
        research infrastructures);

@@

    \item Give an indication of the magnitude and importance of the project's
    contribution to the expected outcomes and impacts, should the project be
    successful. Provide quantified estimates where possible and meaningful.

    ``Magnitude'' refers to how widespread the outcomes and impacts are likely
    to be. For example, in terms of the size of the target group, or the
    proportion of that group, that should benefit over time.

    ``Importance'' refers to the value of those benefits. For example, number of
    additional healthy life years; efficiency savings in energy supply.
\end{itemize}

### 2023-05-02 msca-pf-part-b2-template.tex
add msclongtable wrapper
rename project to msca-pf
update to 2023 call and v3 of the template

\begin{msctable}{
    |>{\ra}p{0.3\linewidth}
    |>{\ra}p{0.66\linewidth}|}
\hline
\multicolumn{2}{|l|}{
    \textbf{[Role]}
} \\
\hline
\multicolumn{2}{|l|}{
    \textbf{[Full name + Legal Entity Short Name + Country]}
} \\
\hline
\multicolumn{2}{|l|}{
    \textbf{General description}
} \\
\hline
\textbf{Role and profile of supervisor} & \\
\hline
\textbf{Key research facilities, infrastructure and equipment} &
Demonstrate that the beneficiary has sufficient facilities and infrastructure to host and/or offer a suitable environment for training and transfer of knowledge to the recruited experienced researcher.

If applicable, indicate the name of the associated partner linked to a beneficiary and describe the nature of the link in the corresponding table. \\
\hline
\textbf{Previous and current involvement in EU-funded research and training
programmes/actions/projects} &
Indicate up to 5 relevant EU, national or international research and training
actions/projects in which the institution/department has previously participated
and/or is currently participating. \\
\hline
\end{msctable}

@@

\section{Letter(s) of commitment from as
    sociated partners (only for hosts of
    outgoing phase of Global Fellowships or non-academic placement)}

@@

For GF proposals, and for all proposals requesting a non-academic placement,
\emph{the absence of a letter of commitment will render the proposal inadmissible
and the proposal will not be evaluated}.

@@

I undersigned \emph{[title, first name and surname]}, in my quality of
\emph{[role in the organisation]} in \emph{[name of the organisation]} commit
to set up all necessary provisions to participate as associated partner in the
proposal \emph{[proposal number and/or acronym]} submitted to the call
HE-MSCA-PF-2022, should the proposal be funded.

>>>>

\begin{msclongtable}[\small]{
    |>{\ra}p{0.3\linewidth}
    |>{\ra}p{0.66\linewidth}|}
\hline
\multicolumn{2}{|l|}{
    \textbf{[Role]}
} \\
\hline
\multicolumn{2}{|l|}{
    \textbf{[Full name + Legal Entity Short Name + Country]}
} \\
\hline
\multicolumn{2}{|l|}{
    \textbf{General description}
} \\
\hline
\textbf{Role and profile of supervisor} & \\
\hline
\textbf{Key research facilities, infrastructure and equipment} &
Demonstrate that the beneficiary has sufficient facilities and infrastructure to host and/or offer a suitable environment for training and transfer of knowledge to the recruited experienced researcher.

If applicable, indicate the name of the associated partner linked to a beneficiary and describe the nature of the link in the corresponding table. \\
\hline
\textbf{Previous and current involvement in EU-funded research and training
programmes/actions/projects} &
Indicate up to 5 relevant EU, national or international research and training
actions/projects in which the institution/department has previously participated
and/or is currently participating. \\
\hline
\end{msclongtable}

@@

\section{Environmental considerations in light of MSCA Green Charter}

Please explain how the proposed project would strive to adhere to the MSCA Green
Charter\footnotemark{} during its implementation.

\footnotetext{MSCA Green Charter \url{https://ec.europa.eu/msca/green_charter}.
While the MSCA Green Charter is non-binding and adherence to it will not be
subject to evaluation, funded projects are strongly encouraged to take into
account the principles it sets out.}

\section{Required for Global Fellowships only: Letter(s) of commitment from
    associated partners (hosting of the outgoing phase)}

@@

For GF proposals \emph{the absence of a letter of commitment will render the
proposal inadmissible and the proposal will not be evaluated}.

@@

I undersigned \emph{[title, first name and surname]}, in my quality of
\emph{[role in the organisation]} in \emph{[name of the organisation]} commit
to set up all necessary provisions to participate as associated partner in the
proposal \emph{[proposal number and/or acronym]} submitted to the call
HE-MSCA-PF-2023, should the proposal be funded.
